---
title: "Data"
subtitle: "For importing, cleaning, and manipulating datasets."
---

```{r}
#| echo: false
#| message: false
source("R/libraries.R")
source("R/functions.R")
```

## Introduction

Here's where I will import my data, clean it for processing, and manipulate or recode variables to my liking. This might also be a good place to link to the codebook or repeat the contents of the codebook here.

## Data Import

Time to import my data and get to work!

```{r}
df_raw <- read.csv("data/validation.csv", header = T)

# Create a sample dataframe
df <- data.frame(
  sex = c(1,2,1,2),
  pas = c(0,1,0,1)
)

df <- df %>% 
    set_variable_labels(
    sex = "Participant sex", 
    pas = "Passed test"
    ) %>%
    set_value_labels(
        sex = c(
            Male = 1, 
            Female = 2,
            Missing = -9
            ), 
        pas = c(
            Fail = 0, 
            Pass = 1
            )
            )

memisc::codebook(df)
```

## Data Cleaning

This is a good place to handle missing data or de-identify data.

```{r}
df <- df_raw |>
    select(-id)
```

## Data Manipulation

Every good dataset needs some averages or sums, and we all need to recode a variable or two.

``` {r}
df <- df |>
    rowwise() |>
    mutate(job_knowledge_total = sum(jk1,jk2,jk3)) |>
    ungroup() |>
    mutate(job_knowledge_quintile = ntile(job_knowledge_total,5))

df$sex_factor <- df$male |>
    recode( 
        `0` = "Female", 
        `1` = "Male"
        ) 
```

## Data Export

People like to have their data in hand. Keeping it in an `.Rdata` file is great as you can keep the data labelled, but the `.csv` file is ubiquitous.

``` {r}
save(df, file = "data/validation_final.Rdata")
write.csv(df, "data/validation_final.csv")
```